The platform's functionality is exposed through a set of RESTful APIs, enabling seamless integration between the frontend and the microservices.

\subsection*{Core Application Flow}
\begin{enumerate}
    \item A prospective adopter visits the site and calls the \textit{PetManagementApi} to retrieve a list of available dogs.
    \item The user registers/logs in via the \textit{UserManagementApi}, receiving an authentication token.
    \item The user initiates the 3-click adoption process. The frontend submits a request to the \textit{AdoptionManager}.
    \item The \textit{AdoptionManager} persists the application in Cosmos DB and publishes an \texttt{AdoptionRequested} event to the Azure Service Bus.
    \item The \textit{NotificationService} consumes the event and sends a confirmation email to the user and an alert to the shelter.
    \item Once the shelter processes the request, the status is updated, triggering another event that notifies the user of the final decision.
\end{enumerate}

\subsection*{Key API Endpoints}
\begin{itemize}
    \item \textbf{UserManagementApi}
    \begin{itemize}
        \item \texttt{POST /api/users/register}: Registers a new user.
        \item \texttt{POST /api/users/login}: Authenticates a user and returns a JWT.
    \end{itemize}
    
    \item \textbf{PetManagementApi}
    \begin{itemize}
        \item \texttt{GET /api/pets}: Retrieves a paginated list of pets with optional search parameters.
        \item \texttt{GET /api/pets/\{id\}}: Retrieves detailed information and image URLs for a specific pet.
        \item \texttt{POST /api/pets}: (Admin only) Adds a new pet listing and uploads images to Azure Blob Storage.
    \end{itemize}
    
    \item \textbf{AdoptionManager}
    \begin{itemize}
        \item \texttt{POST /api/adoptions}: Submits a new adoption application.
        \item \texttt{GET /api/adoptions/user/\{userId\}}: Retrieves all applications for a specific user.
        \item \texttt{PUT /api/adoptions/\{id\}/status}: (Admin only) Updates the status of an application (e.g., Approved, Rejected).
    \end{itemize}
    
    \item \textbf{ReviewService}
    \begin{itemize}
        \item \texttt{POST /api/reviews}: Submits a review for a completed adoption.
        \item \texttt{GET /api/reviews/shelter/\{id\}}: Retrieves all reviews for a specific shelter.
    \end{itemize}
\end{itemize}
